### 2017-08-31 Risk analysis/Text/Layout/Layout/chapter2_methods.tex
trying to write MCMC part

        \subsection{Markov Chain Monte Carlo sampling (MCMC)}
        Despite the apparent simplicity of the Bayes Theorem, a direct analytical calculation and exact inference of the posterior distribution P(A$|$X) is rarely possible in non-idealized cases, due to intractability in high-dimensional spaces \citep{homan2014no, delaVarga2016}.

        - how to obtain posterior parameter distribution
        - intractability of multi-dimensional space makes analytical calculation impossible (directly) --> need for MCMC
        - MCMC: exploration of target distribution by sampling, then accepting or rejecting
        - here used: adaptive Metropolis

>>>>

        \subsection{Markov chain Monte Carlo sampling (MCMC)}
        Despite the apparent simplicity of the Bayes Theorem, a direct analytical calculation and exact inference of the posterior distribution P(A$|$X) is rarely possible in non-idealized cases, due to intractability in multi-dimensional spaces \citep{hoffman2014no, delaVarga2016}. Thereby arises the necessity to resort to methods of statistical inference approximation. Markov chain Monte Carlo (MCMC) sampling has proven to be a generally applicable and reliable method for exploring multi-dimensional parameter spaces in an intelligent way \citep{hoffman2014no, davidson2015}. \citet{gilks2005mcmc} has emphasized the significance of MCMC for the application of Bayesian statistics.
        %In Monte Carlo integration, random samples are drawn from a target distribution, such as our posterior distribution P(A$|$X), to approximate the integral or probability density function in terms of an expectation:

        %\begin{equation}\label{eq:MonteCarlo}
        %        E[P(A|X)] \approx \frac{1}{N}\sum_{n=1}^{N}P(A|X)
        %\end{equation}
        In the ordinary Monte Carlo approach, random independent samples are drawn from a target distribution in order to approximate its shape \citep{gilks2005mcmc}. High-dimensional spaces as found in Bayesian applications lead to complex shapes and often make independent sampling infeasible \citep{gilks2005mcmc}. This can be solved by extending the Monte Carlo principle with a Markov chain, in which every sample iteration of the parameter $\theta^i$ is dependent uniquely on the previous value $\theta^{(i-1)}$ \citep{gilks2005mcmc, delaVarge2016}.
        Various algorithms for random MCMC walks have been developed over more than six decades and are still an active field of research. Common examples are the Metropolis-Hastings (devised by \citet{metropolis1953equation} and continued by \citet{hastings1970}) and the Gibbs sampler \citep{geman1984stochastic}.
        In this work, an adaptive Metropolis-Hastings sampling method is used.
